Lexicographic exponentiation: An example of proof documentation with Alectryon

### 2021-11-24 doc/tuto-beamer.tex
experiments with beamer

\documentclass{article}

@@

\begin{document}
\maketitle

\section{Introduction}
We show a small but non-trivial example of using Alectryon
for writing a documentation (in pdf) of a proof written in Coq.

\section{Preliminaries}
We prove that, if a type $A$ is well founded for a relation \textit{<},
then the set of sorted (w.r.t. the relation $\geq$ ) sequences on $A$  is well-founded too.
Such sequences are represented in a compact way as multisets over $A$. 
For instance, $\langle a,a,a,b,c,c,c,c,c \rangle $ where $a>b>c$ is represented by the list \texttt{(a,2)::(b,0)::(c,4)::nil}.

>>>>

\documentclass[10pt]{beamer}

@@

\begin{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}
  \maketitle
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}
  \frametitle{Introduction}
  \begin{block}{}
We show a small but non-trivial example of using Alectryon
for writing a documentation (in pdf) of a proof written in Coq.    
  \end{block}

  \begin{block}{}
    \begin{quote}

     `` If a   relation $<$ on a type $A$ is well founded,
    then the lexicographic exponentiation of $<$  is well-founded too.''
    \end{quote}

 \end{block}
\end{frame}

\begin{frame}[fragile]

\begin{scriptsize}
\inputsnippets{MultisetWf/AGiven, MultisetWf/lexpowerDef}  
\end{scriptsize}

\begin{footnotesize}
\inputsnippets{MultisetWf/AGiven, MultisetWf/lexpowerDef}  
\end{footnotesize}

\end{frame}

\begin{frame}[fragile]
     The current goal is universally quantified over \texttt{n}.
Thus we may prove it by well founded induction over \texttt{nat}.

\begin{footnotesize}
\inputsnippets{MultisetWf/LAccsc}
  \end{footnotesize}
\begin{footnotesize}
  \inputsnippets{MultisetWf/LAccsd}
\end{footnotesize}

\end{frame}
\end{document}
\maketitle

Such sequences are represented in a compact way as multisets over $A$. 
For instance, $\langle a,a,a,b,c,c,c,c,c \rangle $ where $a>b>c$ is represented by the list \texttt{(a,2)::(b,0)::(c,4)::nil}.
